The Concurrent Calculi Formalisation Benchmark

### 2024-02-23 short-paper/short-paper.tex
Clean up the future work and conclusion section.

% We previously promise to discuss combinations of techniques and applications to more elaborate schemes
%\section{Going Beyond the Challenge Problems}\label{sec:going-beyond}
\section{Future Work and Conclusion}\label{sec:going-beyond}
\todo{Clean up this section to be more coherent.}
Our benchmark challenges do not cover all issues in the field, but focus on the fundamental textbook aspects of linearity, scope extrusion, and coinduction.
Many mechanisations need to combine techniques to handle several of these aspects, and some may also need to handle aspects that are not covered by our benchmark challenges at all.

% \cite{Brady2017} notes that using algebraic effects is unwieldy when there are many communication channels and suggests an experimental approach using dependent uniqueness types.
% \cite{Zalakain2019} notes that systems lacking linear types must simulate linearity, and that using a linearity predicate complicates congruences.
% They had to limit themselves to an asymmetric structural precongruence to be able to prove subject reduction.
Some authors have already described the difficulties that combining techniques may induce in a mechanisation, \eg~\cite{DBLP:conf/forte/ZalakainD21}.

Features that are in wide use, but not covered by our benchmark, include choice constructs and recursion.
Some interesting aspects of message-passing calculi include multiparty session types~\cite{10.1145/2827695} and choreographies~\cite{Carbone2013}, as their meta-theory includes aspects---\eg well-formedness conditions on global types, partiality of end-point projection function, \etc---that we do not address.
Other areas of interest include higher-order calculi~\cite{Hirsch2022}, conversation types~\cite{DBLP:journals/tcs/CairesV10}, psi-calculi~\cite{lmcs:696}, or encodings between different calculi~\cite{DBLP:journals/iandc/Gorla10,DBLP:journals/iandc/DardhaGS17}.

For coinduction, one could explore different notions of process equivalence.

Coinduction may also play a relevant role in supporting recursive processes and session types.
Indeed, it is often the case that session type systems with recursive session types are naturally expressed in \emph{infinitary form} by interpreting their typing rules
coinductively~\cite{DerakhshanPfenning22,HornePadovani23}.

Finally, another interesting avenue to explore would be to take
advantage of certain proof assistant features: for example, extracting
certified implementations (as in \cite{Castro-Perez2021}) or exploiting
proof automation, such as the one offered by the \emph{Hammer}
protocol~\cite{BohmeN10,CzajkaK18}.

Ultimately, our challenges can be extended in several worthwhile directions, and we look forward to a future where they indeed are.
It is our hope and aim that our challenges will move us closer to a future where the key basic proof techniques for concurrent calculi are as easy to mechanise as they are to write on paper.

>>>>

% We previously promise to discuss combinations of techniques and applications to more elaborate schemes
%\section{Going Beyond the Challenge Problems}\label{sec:going-beyond}
\section{Future Work and Conclusion}\label{sec:going-beyond}
Our benchmark challenges do not cover all issues in the field, but focus on the fundamental aspects of linearity, scope extrusion, and coinduction.
Many mechanisations need to combine techniques to handle several of these aspects at once, and some may also need to handle aspects that are not covered by our benchmark challenges at all.

%%% Combinations
Combining techniques for mechanising the fundamental aspects covered in our benchmark is often not trivial.
While we have chosen to focus on the aspects individually to simplify the challenges, we are of course also interested in exploring how techniques interact.
Some authors have already described the difficulties that combining techniques may induce in a mechanisation, \eg~\cite{DBLP:conf/forte/ZalakainD21}.\todo{Add more references here?}

%%% Other aspects
Much current research on concurrent calculi includes aspects that are not covered by our benchmark challenges.
Features that are in wide use, but not covered by our benchmark, include choice constructs and recursion.
Some interesting research topics that build on the fundamental aspects in our benchmark include multiparty session types~\cite{10.1145/2827695}, choreographies~\cite{Carbone2013}, higher-order calculi~\cite{Hirsch2022}, conversation types~\cite{DBLP:journals/tcs/CairesV10}, psi-calculi~\cite{lmcs:696}, and encodings between different calculi~\cite{DBLP:journals/iandc/Gorla10,DBLP:journals/iandc/DardhaGS17}.
Their meta-theory includes aspects---\eg well-formedness conditions on global types, partiality of end-point projection functions, \etc---that we do not address.

Our coinduction challenge only includes two notions of process equivalence, but many more exist in the literature.
Coinduction may also play a role in recursive processes and session types: recursive session types can be expressed in \emph{infinitary form} by interpreting their typing rules coinductively~\cite{DerakhshanPfenning22,HornePadovani23}.

Unlike POPLMark, we consider \emph{animation} of calculi (as in \cite{Castro-Perez2021}) out of scope for our benchmark.
Finally, our challenges encourage, but do not require, exploring proof automation, as offered by \eg the \emph{Hammer} protocol~\cite{BohmeN10,CzajkaK18}.

%%% Conclusion
Ultimately, the fundamental aspects covered by our benchmark serve as the building blocks for most current research on concurrenct calculi.
It is our hope and aim that exploring solutions to our challenges will move the community closer to a future where the key basic proof techniques for concurrent calculi are as easy to mechanise as they are to write on paper.
